Development of a Reinforcement Learning Enabled Cattle Tracker Prototype

### 2025-02-16 paper/main.tex
update the main.tex and ref

\begin{table}[h]
  \centering
  \caption{Reward function parameters, their descriptions, and values extracted during hyperparameter tuning.}
  \begin{tabular}{l p{8cm} c}
      \toprule
      \textbf{Parameter} & \textbf{Description} & \textbf{Value} \\
      \midrule
      reward\_power\_loss & reward for losing power & 0.00  \\ 
      reward\_power\_multiplier & reward per power level at every time step & 0.0001  \\ 
      reward\_action\_0 & reward for doing nothing & -1.716 \\ 
      reward\_action\_1 & reward for collecting and storing data & -0.600 \\ 
      reward\_action\_2 & reward for collecting and transmitting data & -1.485 \\ 
      reward\_message\_count & reward for each message at transmission & 0.841 \\ 
      \bottomrule
  \end{tabular}
  \label{tab:reward_parameters}
\end{table}

@@

\begin{table}[h!]
  \centering
  \caption{Hardware List for the Cattle Tracker Prototype}
  \begin{tabular}{|l|l|l|}
  \hline
  \textbf{Hardware} & \textbf{Serial Number} &  \textbf{Description} \\ \hline
  Arduino MKR WiFi 1010 & ABX00023 &  WiFi-enabled microcontroller board \\ \hline
  Arduino MKR GPS Shield & ASX00017 &  Integrated GPS module \\ \hline
  DFRobot Solar Power Manager & TPX00046 &  Manages and distributes solar cell and battery \\ \hline
  Solar Panel & TPX00181 &  75x100x2.9 mm panel, 1W output \\ \hline
  Sparkfun Fuel Gage & 1568-1273-ND & Analog sensor for power measurement \\ \hline
  LiPo Battery & 2528 &  3.7V, 2000mAh capacity \\ \hline
  \end{tabular}
  \label{tab:hardware_inventory}
  \end{table}

@@

\begin{figure}[h]
  \centering
  \begin{subfigure}{0.48\textwidth}
      \centering
      \includegraphics[width=0.75\linewidth]{./figs/prototype.png}
      \caption{Prototype power level over a 9 day collection window}
      \label{fig:prototype_real}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.48\textwidth}
      \centering
      \includegraphics[width=\linewidth]{figs/prototype_diagram.png}
      \caption{Overall architecture of the reinforcement learning-enabled cattle tracker}
      \label{fig:prototype_diagram}
  \end{subfigure}
  \caption{Prototype of the reinforcement learning-enabled cattle tracker. The device consists of a solar panel for power harvesting, a rechargeable battery, and an embedded microcontroller for decision-making and communication.}
  \label{fig:prototype}
\end{figure}

@@

\begin{table}[h]
  \centering
  \begin{tabular}{lcc}
      \toprule
      & Baseline Agent & RL Agent \\
      \midrule
      Transmission Actions & 480 & 308 \\
      Collection Actions & 480 & 652 \\
      Sleep Actions & 0 & 0 \\
      Avg. Message Count & 756.5 & 789.5 \\
      Avg. Power Level & 34 & 76 \\
      \bottomrule
  \end{tabular}
  \caption{Comparison of Baseline Agent and RL Agent}
  \label{tab:agent_comparison}
\end{table}

>>>>

\begin{table}[h]
  \centering
  \caption{Reward function parameters, descriptions, and values extracted during hyperparameter tuning.}
  \begin{tabular}{l p{8cm} c}
      \toprule
      \textbf{Parameter} & \textbf{Description} & \textbf{Value} \\
      \midrule
      reward\_power\_loss & reward for losing power & 0.00  \\ 
      reward\_power\_multiplier & reward per power level at every time step & 0.0001  \\ 
      reward\_action\_0 & reward for doing nothing & -1.716 \\ 
      reward\_action\_1 & reward for collecting and storing data & -0.600 \\ 
      reward\_action\_2 & reward for collecting and transmitting data & -1.485 \\ 
      reward\_message\_count & reward for each message at transmission & 0.841 \\ 
      \bottomrule
  \end{tabular}
  \label{tab:reward_parameters}
\end{table}

@@

\begin{table}[h]
  \centering
  \caption{Hardware list for the cattle tracker prototype}
  \begin{tabular}{l p{8cm} c}
      \toprule
      \textbf{Hardware} & \textbf{Description} & \textbf{Serial Number} \\
      \midrule
      Arduino MKR WiFi 1010 & WiFi-enabled microcontroller board & ABX00023 \\
      Arduino MKR GPS Shield & Integrated GPS module & ASX00017 \\
      DFRobot Solar Power Manager & Manages and distributes solar cell and battery & TPX00046 \\
      Solar Panel & 75x100x2.9 mm panel, 1W output & TPX00181 \\
      Sparkfun Fuel Gage & Analog sensor for power measurement & 1568-1273-ND \\
      LiPo Battery & 3.7V, 2000mAh capacity & 2528 \\
      \bottomrule
  \end{tabular}
  \label{tab:hardware_inventory}
\end{table}

@@

\begin{figure}[h]
  \centering
  \begin{subfigure}[t]{0.48\textwidth}  % Align top
      \centering
      \includegraphics[height=6cm, keepaspectratio]{./figs/prototype.png}
      \put(-170,160){\scriptsize \textbf{(A)}}  % Adjust position as needed
      \label{fig:prototype_real}
  \end{subfigure}
  \hspace{2mm}  % Reduce space between figures
  \begin{subfigure}[t]{0.48\textwidth}  % Align top
      \centering
      \includegraphics[height=6cm, keepaspectratio]{./figs/prototype_diagram.png}
      \put(-215,160){\scriptsize \textbf{(B)}}  % Adjust position as needed
      \label{fig:prototype_diagram}
  \end{subfigure}
  \caption{Prototype of the reinforcement learning-enabled cattle tracker. (A) Physical prototype with hardware components. (B) System architecture diagram illustrating data processing and power management.}
  \label{fig:prototype}
\end{figure}

@@

\begin{table}[h]
  \centering
  \caption{Comparison of baseline agent and RL agent}
  \begin{tabular}{lcc}
      \toprule
      & Baseline Agent & RL Agent \\
      \midrule
      Transmission Actions & 480 & 308 \\
      Collection Actions & 480 & 652 \\
      Sleep Actions & 0 & 0 \\
      Avg. Message Count & 756.5 & 789.5 \\
      Avg. Power Level & 34 & 76 \\
      \bottomrule
  \end{tabular}
  \label{tab:agent_comparison}
\end{table}
